Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-12-11 1.Paper/Paper.Rmd
Updated toy example and mice.impute.2l.2stage

The Heckman 2L imputation method is available in the micemd R package [@audigier2021] (as \textbf{mice.2l.heckman()}) and also on the github repository \url{https://github.com/johamunoz/Statsmed_Heckman} where you can also find all the codes accompanying this paper and a toy example that explains how to implement the method in mice.

>>>>

The Heckman 2L imputation method is available in the micemd R package [@audigier2021] (as \textbf{mice.2l.2stage.heckman()}) and also on the github repository \url{https://github.com/johamunoz/Statsmed_Heckman} where you can also find all the codes accompanying this paper and a toy example that explains how to implement the method in mice.
